New lower bounds for Schur and weak Schur numbers

### 2021-06-12 article/schur.tex
qq typos + biblio

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of Figure 1 not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
table.

@@

\qquad We start by reminding the explicite construction of a sum-free partition with the use of a S-template and another sum free partition. We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.

@@

\subsection{New lower bounds for Schur numbers}
\label{Subsection2.3}
We now give the inequalities correspondng to the current  best S-templates (to our knowledge).

@@

We produced S-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
\((a, b)\) (in the lexicographic order). When the number of colors excceeded five, in order to reduce the search space we 
only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.

@@

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement proabably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
by combining a S-template with width 380 and one with width three. Although we could not find a better S-template with seven 
colors, inequality (\ref{S(n+6)}) can definitely be improved by a wide margin. One may try to seek better templates by 
constraining less the search space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject 
of a future work.

>>>>

We begin by introducing \textit{S-templates}, standing for \textit{"Schur templates"}. The idea is to consider the first line
of \hyperref[figure:1]{Figure 1} not as a combination of two blocs anymore but as a whole, single construction. We thereby define a S-template as
a new object filling the role of the first line but with less, yet sufficiant, constraints that will allow the expansion of the
table.

@@

\qquad We start by reminding the explicit construction of a sum-free partition with the use of a S-template and another sum free partition. We apply this contruction stated by Rowley in the context of Ramsey numbers to the Schur numbers.

@@

\subsection{New lower bounds for Schur numbers}
\label{Subsection2.3}
We now give the inequalities corresponding to the current  best S-templates (to our knowledge).

@@

We produced S-templates using a SAT solver, hence providing lower bound on \(S^+\) and inequalities 
of the type \(S(n+k) \geqslant a S(n) + b\). We sought templates providing the largest value of 
\((a, b)\) (in the lexicographic order). When the number of colors exceeded five, in order to reduce the search space we 
only looked for symmetric S-templates, we assumed that the special color was the last color to appear and we constrained 
the \(m_c\)'s out of being too small. Details concerning the encoding as a SAT problem can be found in \cite{Heule2017}.

@@

\par
Inequalities (\ref{S(n+1)}), (\ref{S(n+2)}) and (\ref{S(n+3)}) cannot be further improved (with this definition of S-template). 
Inequality (\ref{S(n+4)}) cannot be further improved by only searching for symmetric S-templates whose special color is the 
last in the order of apparition (and with a multiplicative factor less than or equal to 118). Inequality (\ref{S(n+5)}) can most 
likely be further improved but the improvement probably will not be substantial. Finally, inequality (\ref{S(n+6)}) is obtained 
by combining a S-template with width 380 and one with width three. Although we could not find a better S-template with seven 
colors, inequality (\ref{S(n+6)}) can definitely be improved by a wide margin. One may try to seek better templates by 
constraining less the search space and by using Monte-Carlo methods, as in \cite{Bouzy2015AnAP}. This could be the subject 
of a future work.
